\begin{abstract}

In daily life, it is necessary to get specific persons' images on various occasions.
For example, pass the portrait information of strangers and get an image of a person different from the state in picture.
As usual, oral description or drawing sketch map are generally adopted,
    which has poor real-time performance, high requirements for users,
    passing information not intuitive and easy leading to deviation.
Nowadays, machine learning grows fast.
It makes it significant to use machine learning to meet the need of facial image generation and adjustment whether in technical research or practical application.
However, due to the huge size of models as well as the high training, deployment, and running use-cost,
    machine-learning models of facial image generation and adjustment have rarely been applied to production activity.
As a result, our research tried to use and improve the development of Generative Adversarial Networks(GAN)\upcite{gan},
    aiming to reduce the model size so that the computational load in training and runtime is cut down,
    along with fine performance. 

Through a large scale of experiments, we propose "Single model for facial generation and adjustment",
    which is a multi-task model, capable of achieving functions including facial attribute identification, 
    conditional facial image generation and adjustment.
In this work, we develop a model based on DCGAN\upcite{dcgan},
    inspired by pix2pix\upcite{pix2pix} and PGGAN\upcite{pggan}.
Major improvements are as follows.
We share parameters between auto-encoder and part of GAN,
    reducing the size of the model and use-cost compared to two individual models.
Aiming to reduce the loss of original image information, we adjust images in the image space.
We also propose a method of part training, making it possible to train deep network easily.

It is validated that the model can validly generate plausible images of faces from attributes and be adjusted by the certain condition.
Results also suggest that the use-cost of models has declined compared to DCGAN\upcite{dcgan} and pix2pix\upcite{pix2pix},
    which can be effectively applied to the actual production activity. 

    \begin{IEEEkeywords}
        Facial Image Generation, Facial Image Adjustment, Generative Adversarial Networks, Machine Learning
    \end{IEEEkeywords}

\end{abstract}