\section{Introduction}
As an important characteristic, face makes a difference in the interpersonal activities.
In daily life, it is necessary to get specific persons' images on various occasions.
For example, pass the portrait information of strangers and get an image of a person different from the state in picture.
In recent years, machine learning has gone deeply in the society.
Facial image generation and adjustment are one of the directions.

Combined with the technology of facial identification, facial image generation can be used to determine identity.
The technology mainly applies to identity verification, used to chase the target, which is a vital auxiliary method to combat criminal activities.
When it comes to social activities, it can also be utilized to the identification in intelligent interaction scene. For example, the security check at the school gate and the check point of the company.

Nowadays, under the circumstances of the disability to get the exact figure,
    public safety agency mainly adopt the following method.
According to the description of eyewitness, corporate with the painter to get the rough facial image,
    search for the figure in the existing image data base and determine the identity of the figure.
We assume that the method has large shortcomings.
First, the perspective of the painter will affect the generation of the portrait.
    Second, there will be high requirements for users.
    Third, the method has poor real-time performance.
According to the photo of target person, the method of tracking and positioning may also cause the face of the target person to be inaccurate .It may be due to the problem of poor photographing angle or the long time of taking photos.
The research on adjusting the attribute of the facial image is used to solve this problem.
This research has certain practical significance in the fields, which need the images of accurate target figures more quickly. For example, accurate positioning targets in criminal investigation and improve the speed of solving crimes.