\section{Target and Innovation}

In order to provide a more suitable solution for facial image generation and adjustment,
    we use machine learning technology to study.

\subsection{Research Target}
\begin{itemize}
\item Explore the use of machine learning technology to propose a workable, convenient and efficient method.
    Provide a new solution to the needs of facial image generation and adjustment to make up for traditional means such as hand-painting and manual use of software to modify images or other technical means.
\item Combine specific problems and cutting-edge research results.
    Innovate and improve the model and training methods based on the existing research.
    Reduce the volume of the model and reduce the cost of model use.
\item Use new methods to adjust the image so as to reduce the information loss of the original image during the adjustment process.
\end{itemize}
\subsection{Research Innovation}
\begin{itemize}
\item Use facial image generation and adjustment model proposed by machine learning technology.
    Compared with the traditional method of artificially sketching images, the image acquisition speed is faster, the requirements for the user are lower,
    and the scalability is higher as well as mobility.
\item Propose a model based on GAN\upcite{gan} for conditional facial image generation and adjustment.
    Three tasks of facial image attribute recognition,
    conditional generation and conditional adjustment can be completed by one model.
    Effectively reduce the consumption of the computing resources by the training,
    the model volume and the calculation amount at the runtime.
    Achieve the purpose of reducing the training, deployment, and running cost of the model.
\item To solve the problem that the deep neural network is too deep in the network and the gradient of the previous network layer in the back propagation process is too small to be effectively adjusted,
    we propose and apply the part training method to speed up the network convergence speed and further reduce the amount of calculations for training.

\item Our model adjusts the facial image in the image space to reduce the loss of the original image information during the adjustment.
\end{itemize}